Causal Compatibility Inequalities Admitting Quantum Violations in the Triangle Structure

### 2020-06-02 CCIAQVTS/CCIAQVTS.tex
changed the wagon wheel inequality to the correct one, and changed the violation amount to the correct one
added an Acknowledgement to Chaves for spotting the error with the Wagon-Wheel inequality

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        +P_{A_{l}B_{l}}(11) -P_{A_{l}B_{l}C_{l}C_{r}}(1111) +P_{A_{l}B_{l}}(00) P_{C_{l}C_{r}}(11) +P_{C_{l}C_{r}}(01) P_{C_{l}C_{r}}(10) \\
        -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000) -P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001) -P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110) -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111) +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        \leq 0
    \end{gathered}
    \end{equation*}

    \Cref{eq:ww_ineq} is termed the Wagon Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}. Moreover, note that \Cref{eq:ww_ineq} is reported using the same two-bit notation discussed in~\cref{sec:fritz_distribution} such that $\prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}] = \prob[ABC][abc]$.

@@

    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$. On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16} \not \leq 0$. Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.

@@

    \begin{acknowledgments}
    This research was supported in part by Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science. The authors are grateful to Miguel Navascués and Denis Rosset for their insightful discussions.
    \end{acknowledgments}

>>>>

    \subsection{The WagonWheel Inequality}
    The first causal compatibility inequality chosen for presentation is reported below:
    \begin{equation*}
    \begin{gathered}
        \eq\label[ineq]{eq:ww_ineq}
        I\tsb{WagonWheel} : \\
        -P_{A_{l}B_{l}}(10)
        +P_{A_{l}B_{l}C_{l}C_{r}}(1010)
        -P_{A_{l}B_{l}}(01) P_{C_{l}C_{r}}(10)
        -P_{C_{l}C_{r}}(00) P_{C_{l}C_{r}}(11) \\
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(100110)
        -P_{C_{l}C_{r}}(01) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(110010) \\
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(101111)
        +P_{C_{l}C_{r}}(00) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(111011) \\
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(001001)
        +P_{C_{l}C_{r}}(10) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(011101) \\
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(000000)
        +P_{C_{l}C_{r}}(11) P_{A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}}(010100) \\
        \leq 0
    \end{gathered}
    \end{equation*}

    \Cref{eq:ww_ineq} is termed the Wagon-Wheel inequality and denoted $I\tsb{WagonWheel}$ after the (identically-named) inflated structure of \cref{fig:wagon_wheel_inflation} used to derive it. To reiterate, a summary of the methods used to derive \cref{eq:ww_ineq} can be found in \cref{sec:marginal_satisfiability,sec:inflation_technique_summary,sec:deriving_inequalities}. Moreover, note that \Cref{eq:ww_ineq} is reported using the same two-bit notation discussed in~\cref{sec:fritz_distribution} such that $\prob[A_{l}A_{r}B_{l}B_{r}C_{l}C_{r}][a_{l}a_{r}b_{l}b_{r}c_{l}c_{r}] = \prob[ABC][abc]$.

@@

    By construction, every distribution $\prob[ABC]$ that is compatible with the Triangle structure per \cref{eq:triangle_compatibility} must satisfy $I\tsb{WagonWheel}$. On the other hand, the Fritz distribution violates $I\tsb{WagonWheel}$ with violation $\f{1}{16}(\sqrt{2} - 1) \not \leq 0$. Consequently we affirm that the Fritz distribution is incompatible with the Triangle structure, a fact previously only demonstrated without inequalities.

@@

    \begin{acknowledgments}
    This research was supported in part by Perimeter Institute for Theoretical Physics. Research at Perimeter Institute is supported by the Government of Canada through the Department of Innovation, Science and Economic Development Canada and by the Province of Ontario through the Ministry of Research, Innovation and Science. The authors are grateful to Miguel Navascués and Denis Rosset for their insightful discussions. The authors would like to thank Rafael Chaves for identifying an error with the Wagon-Wheel inequality found in earlier versions of this paper.
    \end{acknowledgments}
